\documentclass[a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath, amssymb, amsthm, amsfonts}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}

\title{Math Camp}
\author{Hyoungchul Kim}


\begin{document}
\maketitle
	

\section{Day 1}

\textbf{Important notes}

\begin{itemize}
	\item Due to housing issue, I might have to miss the first day.
	\item Due to this problem, I will be manually studying for about 5 to 6 subsections using the notes given by the instructor.
\end{itemize}


\noindent \textbf{Short notes in class}

\begin{itemize}
	\item Part 1: real calculus.
	\item Part 2: linear algebra.
	\item Part 3: probability and optimization.
	\item Each part lasts two weeks.
	\item HW assignment every week but not graded.
	\item Friday: Quiz (2 hours).
	\item Only thing that matters is math camp exam: Mostly everyone passes if one takes classes.
	\item Communication done through canvas.
	\item Part 1 deals with mathematical logic, spaces (metrics, topology), correspondence.
\end{itemize}

\textbf{Some notation}\\

$\N$: Natural numbers.

$\Z$: Integer numbers.

$\Q$: Rational numbers.

$\R$: Real numbers.\\

\textbf{Binary relation}\\

Binary relation $R$ on set  $X$ is a subset of  $X\times X$.

\begin{enumerate}
	\item $R$ is reflexive if:  $\forall x \in X, \, xRx$
	\item $R$ is symmetric if:  $\forall x, y \in X, \, xRy \implies yRx$
	\item $R$ is transitive if:  $\forall x, y \in X, \, xRy, yRz \implies xRz$
\end{enumerate}

\noindent \textbf{Def:} A binary relation is an equivalence relation if it is reflexive, symmetric and transitive. We denote this as $x\sim y.$\\

\noindent \textbf{Def:} $R$ is antisymmetric if  $\forall x, y \in  X, xRy \text{ and }  yRx \implies x=y.$\\

\noindent \textbf{Def:} $R$ is partial order on $X$ if it is reflexive, antisymmetric and transitive.\\ 

\noindent \textbf{Def:} $x, y \in X$ are comparable if $xRy \text{ or } yRx.$\\

\noindent \textbf{Def:} A partial order $R$ is a total order if every two elements are comparable.\\

\noindent \textbf{Def:} $f: X \to Y$ is an injection if $\forall a, b \in X, a \neq b \implies f(a)\neq f(b).$\\ 

\noindent \textbf{Def:} $f: X \to Y$ is an surjection if $Y=f(X)=\{ y \in Y | \exists x \in X: f(x)=y\}.$\\

\noindent \textbf{Def:} $f: X \to Y$ is called bijection if it is both an injection and surjection.\\ 

\noindent \textbf{Fact:} $f: X \to Y$ is an injection if $\forall y \in Y$, $f^{-1}\left( \{y\} \right) $ has no more than one element.\\ 

\noindent \textbf{Fact:} $f: X \to Y$ is an surjection if $\forall y \in Y$, $f^{-1}\left( \{y\} \right) $ has at least one element.\\ 

\noindent \textbf{Fact:} $f: X \to Y$ is an bijection if $\forall y \in Y$, \#$f^{-1}\left( \{y\} \right)=1.$\\ 

\noindent \textbf{Fact:} $f$ have inverse $\iff$ $f$ is a bijection.
\begin{proof}
	i. $f^{-1}$ exists $\implies$ $f$ is a bijection: $f^{-1}\left( \{y\} \right) &= \{ f^{-1}\left( y \right) \} \\$. Assume not $\implies \exists a \in f^{-1}\left( \{y\} \right) \, s.t. a \neq f^{-1}\left( y \right).$ But $f(a)=y \implies f^{-1}\left( f(a) \right) = f^{-1}\left( y \right).$

	ii. $f$ is a bijection $\implies$ $f^{-1}$ exists. Construct $g$ s.t. $g(y)$ is the only element of $f^{-1}\left( \{y\} \right)$. $f \cdot g: f(g(y)) = y; \, g \cdot f: g(f(x))=y$.
\end{proof}\\

\noindent \textbf{Fact:} Bijection between two finite sets exists only if $\#A &= \#B.$ \\

\noindent \textbf{Def:} $A$ and $B$ have equal cardinality if there is a bijection $f: A \to B$.\\

\noindent \textbf{Fact:} Having the same cardinality is an equivalence relation.
\begin{proof}
	i. reflexivity: $id_{A}$ is a bijection.

	ii. symmetry: $f: A \to B$ is a bijection $\implies$ $f^{-1}$ is also a bijection.

	iii. transitivity: $f:A \to B$ and $g:B \to C$ is bijection, then $g \cdot f$ is also bijection.
\end{proof}

\noindent \textbf{Def:} $A$ is denumerable if $\# A = \#\N$. (countably infinite) $A$ is countable if it is finite or denumerable. $A$ is uncountable if it is not countable.\\

\noindent \textbf{Ex:} Show $\N \times \N$ is denumerable.
\begin{proof}
	(0,0), (0,1) \ldots\\
	\indent \indent (1,0), (1,1) \ldots\\
	Just go diagonal. Then it will get you a mapping that is bijection.\\

	$f(m,n) = \frac{(m+n)(m+n+1)}{2}+m$.
\end{proof}

\noindent \textbf{Corr:} $\forall k > 0$, $\N^{k}$ is denumerable.
\begin{proof}
	later.
\end{proof}

\noindent \textbf{Prob:} Let $A \subset B$. $A$ is infinite and $B$ is denumerable. Then $A$ is denumerable.
\begin{proof}
	$f: \N \to B$. $f^{-1}(A) \subset \N$ Later solve it. 
\end{proof}

\noindent \textbf{Corr:} Let $f: A \to B$ be a surjection. If $A$ is denumerable and $B$ is infinite, then $B$ is denumerable.
\begin{proof}
	Later.
\end{proof}

\noindent \textbf{Def:} We say $\# A \le \#B$ if there is an injection $f: A \to B$. If there is no bijection from $A$ to $B$, we can say that the cardinality of $A$ is strictly smaller than that of $B$.\\

\noindent \textbf{Prob:} Prove that $\{0,1\}^{\N}$ is uncountable.
\begin{proof}
	Later. But just use the fact that if denumerable, its element can be written as a sequence.
\end{proof}

\noindent \textbf{Def:} The set of all subsets of $A$ is called power set of $A$ and is noted as $2^{A}$.\\

\noindent \textbf{Prob:} If $A$ is finite $\implies \# 2^{A} = 2^{\# A}$.
\begin{proof}
	Later.
\end{proof}

\noindent \textbf{Theorem} For every $A, \#2^{A} > \#A$.
\begin{proof}
	Injection: $x \to \{x\}$ from $A$ to $2^{A}$.

	Suppose there is a bijection $f: A \to  2^{A}$. $B = \{x \in A | x not\in f(x)\}=2^{A}. \implies \exists y \in A s.t. f(y)=B.$ 

	1. $y \in B \implies y not \in f(y)=B$ by def of $B$.

	2. $y not \in B \implies y \in f(y) =B$ by def of $B$.

	This is contradiction. Thus done.
\end{proof}

\noindent \textbf{Prob:} $\# \R = \# 2^{\N}$.
\begin{proof}
	We show that $[0,1] = 2^{\N}$ in cardinality.
\end{proof}

\noindent \textbf{Prob:} $\forall n \in \N, \R^{n} \sim \R$.
\begin{proof}
	Later.
\end{proof}

\noindent \textbf{Theorem} If $\# A \le \# B$ and vice versa, then the cardinality for both set is same.\\

\noindent \textbf{Some Exercises}\\

\noindent Exercise 1.3.11: Why such partition exists only for equivalence relation? Are all three properties required for existence of such partition?

\begin{proof}
	car
\end{proof}

\noindent Exercise 1.3.20: Let's define a binary relation $R$ on $\N$ in a following way: $xR y$ if $y$ is divisible by $x$. Is this relation a partial order, a total order or it is not order at all?

\begin{proof}
	car
\end{proof}

\noindent Exercise 1.4.10: Define a bijection in a similar way (using preimages). 

\begin{proof}
	car
\end{proof}

\noindent Exercise 1.4.11: Show that $f: X \to Y$ and $g: Y \to Z$ both are bijections, then $g \cdot f: X \to Z$ is a bijection too.

\begin{proof}
	car
\end{proof}

\noindent Exercise 1.4.15: $f: X \to Y$  has an inverse if and only if it is a bijection.

\begin{proof}
	car
\end{proof}


\section{Day 2}

\textbf{PS1 review}\\

PS 1.
\begin{proof}
	This is false. Let $p(x,y) \implies x+y=5$.
\end{proof}

PS 2.
\begin{proof}
	Obvious.
\end{proof}

PS 3.
\begin{proof}
	(i) $xRy \iff x \neq y.$

	(ii) $xRy \iff x < y+1.$

	(iii) $xRy \iff x>y.$
\end{proof}

PS 4.
\begin{proof}
	Obvious.
\end{proof}

PS extra. Set of all ftns on $\R$ $fRg$ if $\forall x \in \R \, f(x) \le g(x).$ Is it a total order, partial order or not an order?
\begin{proof}
	(1) reflexive: $fRf$ 

	(2) transitive: $fRg \, gRh \impliesfRh.$

	(3) antisymmetric.
\end{proof}

PS 5.
\begin{proof}
	No.
\end{proof}

PS 6.
\begin{proof}
	Check my notes in github.	
\end{proof}

PS 7. 
\begin{proof}
	We know that $\N \times \N \sim \N$. We just need to show there is bijection between $\Q \times \N$ and $\N \times \N$. We use the fact there there is bijection from rational number to natural number.
\end{proof}

PS 8.
\begin{proof}
	(iii) Try to use that $\left( 0, 1 \right) \times \N \to \R$ is injection and there is bijection from $\left( 0,1 \right) $ to real number.

	(iv) set of all finite seq of $\N = \cup_{n \in \N} \{ \text{all seq of length n}\}$.
\end{proof}

PS 9.
\begin{proof}
	Later.
\end{proof}

PS 10.
\begin{proof}
	$X$ is set of a possible bijections from one countable set to another.

	(i) Sps $A$ and $B$ have different cardinality $\implies$ zero.

	(ii) If they have same cardinality $m$ : $m!$.

	(iii) If they have same cardinality to  $\N$ : continuum.

	Let $X$ be set of all bijections from natural number to natural number.

	Need to show that $f: 2^{\N} \to X$ and vice versa is injection.
\end{proof}

PS 11.
\begin{proof}
	No. 

	i. $A$ is finite. Then $2^{A}$ is finite.

	ii. If $A$ is infinite. $A\sim \N \implies \# 2^{A} > \N$
\end{proof}

PS 12.
\begin{proof}
	i. $X$ is finite. Then $X = \{0, 1, \ldots, n\}$.
	Later. Just remember to move them or shift them.
\end{proof}

\textbf{Short notes in class}\\

\textbf{Def:} Vector space over $R$ is a nonempty set $V$ on which two binary operations (scalar multiplication and vector addition is defined). It has following properties:
\begin{enumerate}
	\item $u + (v+w)=(u+v)+w.$
	\item $u+w=w+u.$
	\item $\exists 0 \in V s.t.\, u+0=u.$ 
	\item $\exists -u \in V s.t. \, u+(-u)=0.$
	\item $\lambda (\mu v) = (\lambda \mu) v.$
	\item  $1 \cdot u = u.$
	\item $\left( \lambda + \mu \right) u = \lambda u + \mu u.$
	\item $\lambda (u+v) = \lambda u + \lambda v.$
\end{enumerate}

\textbf{Def:} $V$ is a v.s. Then norm can be defined as $ \mid  \mid  \cdot  \mid  \mid : V \to \R_+$.
\begin{enumerate}
	\item $ \mid  \mid u  \mid  \mid = 0 \iff v=0.$
	\item  $\mid \alpha v  \mid  \mid =  \mid \alpha  \mid  \cdot \mid  \mid v  \mid  \mid .$ 
	\item $ \mid  \mid u+v  \mid  \mid  \le   \mid  \mid  v \mid  \mid +  \mid  \mid u  \mid  \mid .$ 
\end{enumerate}

\textbf{Ex.} Let $X = \left( x_1, \ldots , x_{n} \right) \in \R^{n}.$ We can define norm as $ \mid  \mid x \mid  \mid = \sqrt{\sum_{i=1}^{n} X_{i}^{2}}.$\\

\textbf{Note.} Remember that there are many ways to construct norms.\\

\textbf{Def:} A metric on a set $X$ is a function 
\[
d: X \times X \to \R_+, \forall x,y \in X
.\] 
\begin{enumerate}
	\item $d(x,y)=d(y,x).$
	\item $d(x,y)=0 \iff x=y.$
	\item $d(x,z) \le  d(x,y) + d(y,z).$
\end{enumerate}


\textbf{Def:} A metric on a set $X$ is a function
\[
d: X \times X \to \R_+
.\] 

s.t. $\forall x, y \in X,$
\begin{enumerate}
	\item $d(x,y) = d(y,x).$
        \item $d(x,y)=0 \iff x=y.$
	\item $d(x,y) \le d(x,y) + d(y,z).$
\end{enumerate}

\textbf{Def:} A pair $(X,d)$ is called a metric space.\\

\textbf{Ex:} Trivial metric is  $d(x,y)$ where it is 0 if $x=y$ and 1 otherwise.\\

\textbf{Ex:} Normed vector space  $(V,  \mid  \mid \cdot  \mid  \mid )$. In this case, $d(x,y) =  \mid  \mid x-y \mid  \mid $ induces a metric on it.\\

\textbf{Def:} A sequence is basically a function $f: \N \to X$ and we write it as $(x_n) \in X.$\\

\textbf{Def:} A cauchy sequence is a sequence such that: $\forall \varepsilon >0, \exists N, s.t. \, \forall n, m > N, d(x_n, x_m)< \varepsilon.$\\

\textbf{Def:} A sequence $(x_n)$ converges to $x$ if 
\[
\forall \varepsilon > 0, \exists N: \forall i > N, d(x_n, x) < \varepsilon
.\] 

We denote this as $X_n \to x; \, \lim_{n \to \infty}x_n = x.$\\

\textbf{Note:} The convergence is unique. Assume it is not unique and the sequence converge to x and y. Then take $\varepsilon = \frac{d(x,y)}{3}$. There will be some $N$ large enough for some $i$ s.t. $d(x_i, x) < \varepsilon, d(x_i, y) < \varepsilon).$ This implies that  $d(x,y) < 2\varepsilon.$ But this means  $d(x,y) < 2 \varepsilon = \frac{2}{3} d(x,y) \implies \text{contradiction}.$\\

\textbf{Prop:} Every converging sequence is a cauchy sequence. But note that vice versa does not hold generally. Think about $x_n = \frac{1}{n}$ in (0,1).\\

\textbf{Theorem} In $\R$, every cauchy seq. converges.\\

\textbf{Def:} $(X,d)$ is complete if any cauchy seq. converge (e.g. $\R, \R^{n}$ with euclidean metric).\\

\textbf{Ex:} $\Q$ is not complete space. Take any seq. converging to square 2.\\


\textbf{Prop:} $C\left( [a,b] \right) $ with sup metric is a complete space.
\begin{proof}
	Let $f_n$ be a cauchy seq. For $\forall x \in [a,b],  \mid f_n (x) - f_m (x)  \mid  \le  d(f_n, f_m) = \text{max}  \mid f_n (x) - f_m (x)  \mid . \implies \forall x \in [a,b], f_n$ is a cauchy seq. 

	Define $f$ s.t. $\forall x \in [a,b], f(x) = \lim_{n \to \infty} f_n (X) \implies f_n \to f\ldots..$
\end{proof}

\textbf{Def:} Mapping $A:X \to X$ is a contraction if $\exists \lambda \in [0,1)$ s.t. $\forall x, y \in X$ $d\left( A(x), A(y) \right) \le  \lambda \cdot d(x,y)$.\\

\textbf{Def:} $x \in X$ is a fixed point of $A: X \to X$ if $A(x)=x.$\\

\textbf{Theorem (Banach fixed-point thm)} A is a contraction on complete  $(X,d)$. Then $A$ has unqiue fixed point $x^{*} \in X.$ \\


\textbf{Bellman eq.} $V(x) = max_a \left( u(a,x) + \beta V(x') \right) $, $X' = g(a,x).$  $A:f \to max_a \left( u(a,x) + \beta f(x') \right) $.



\end{document}
